\section{Related Work}
\label{sec::relatedwork}
Efficiently computing optimal paths is a topic of interest in the literature
of AI, Algorithmics, Game Development and Robotics. We discuss a few recent
results.

TRANSIT~\cite{bast06} and Contraction Hierarchies~\cite{geisberger08} are two
highly successful algorithms that have appeared in recent years.
Both of these approaches operate on similar principles: they
employ pre-processing to identify nodes that are common to a great many
shortest paths. Pre-processed data is exploited during online search to
dramatically improve pathfinding performance. Though very fast on road networks
these algorithms have been shown to be less performant when applied to grids,
especially those drawn from real computer games;
e.g.~\cite{sturtevant10,antsfeld12,storandt13}.

Swamps~\cite{pochter10} is an optimal pathfinding technique that uses
pre-processing to identify areas of the map that do not need to be searched. A
node is added to a set called a swamp if visiting that node does not yield any
shorter path than could be found otherwise. By narrowing the scope of search
Swamps can improve by several factors the performance of classical pathfinding
algorithms such as A{*}.  Such pruning approaches are orthogonal to much of
the work we develop in this paper. We will revisit the connection in the 
concluding section of this paper.

SUB~\cite{urasKH13} is a recent and very fast technique for computing optimal
paths in grid-map domains.  This algorithm works by pre-computing a grid
analogue of a visibility graph, called a subgoal graph, which it stores and
searches instead of the original (much larger) grid.  A further improvement
involves directly connecting pairs of nodes for which the local heuristic is
perfect (this operation is similar to graph contraction~\cite{geisberger08} in
that it has the effect of pruning any intermediate nodes along the way).  To
avoid a large growth in its branching-factor SUB prunes other additional edges
from the graph but this latter step makes the algorithm sub-optimal in certain
cases. We compare our work against two variants of SUB in the empirical
evaluation section of this paper.

