\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

During my candidature I have been fortunate to work with and receive
guidance from a number of talented individuals. 
Foremost among these are my co-supervisors: Adi Botea, 
Alban Grastien and Philip Kilby. They have each given me so much of their time, 
their patience, their encouragement and their deep expertise that 
I feel I can never repay the debt. They are exceptional individuals and
I have tried at all times to model myself according to their example.  
%Though I do not know to what degree I have succeeded,
Working alongside them and learning from them has shaped me personally and
professionally and I am humbled for having had the opportunity.
\newline \\ 
\noindent 
I owe another great debt to Sylvie Thi{\'e}baux, who has mentored me
throughout my time at ANU and NICTA.  Sylvie is a tireless champion who has opened
many doors and given me many opportunities to interact with and present my
work to eminent individuals from academic and non-academic backgrounds. She
has taught me to be confident, to tell it how it is and to always persevere in
the face of adversity. I am immensely fortunate to have had her in my corner.
\newline \\ 
\noindent
A special thank you to Patrik Haslum for the endlessly stimulating discussions
about AI Planning and Heuristic Search.  Thanks also for the many cigarettes!
\newline \\ 
\noindent
Thank you to my many friends from NICTA and elsewhere who made my time in
Canberra so enjoyable. Special shout-outs to Chris Bennetts-Cash, Adam
Rumbold, Ayman Ghoneim, Nina Narodytska, Debdeep Banerjee, Jason Li,
Pattaraporn Khuwuthyakorn, Cindy Wang, Eddie Li and Zahra Zamani.
\newline \\ 
\noindent
Thank you to my brother, Alex, who constantly reminds me there is a more
amusing side to life. Some of my favourite moments from these last few years have
been while visiting Melbourne and catching up with you.
\newline \\ 
\noindent
I am grateful to my wife, Alina, who encouraged, supported and
otherwise put up with me throughout this long endeavour. Her love has been
like a light, shining brightly always and helping me find my way home.
\newline \\ 
\noindent
Finally, to my parents, Daniel and Elena, who uprooted their lives for the sake
of my brother and I.  You taught me the importance of education, you taught me
drive and ambition, you taught me respect, compassion, forgiveness and love.
You raised me as a boy and then you shaped me into a man. You showed me the
path and I follow it still. Thank you.

