\section{Principle Of Anya}
Consider as a motivating example the problem depicted in Figure~\ref{fig::ex1}.
We are tasked with finding an any-angle path between node $n_1 = (2, 0)$ and
node $n_2 = (3, 4)$.  The best online algorithm for solving this problem, to
date, is Theta*~\cite{nash07}. It operates by looking for a solution among the
set of discrete points that comprise the locations of the grid; i.e.,
it successively expands nodes $(2,1)$ to $(2,4)$ and $(3,0)$ to $(3,3)$ until
eventually $n_2$ is reached.  Notice however that the actual shortest path
between $n_1$ and $n_2$ may not pass through any of these discrete points.  To
account for this fact Theta* ``pulls the string'' each time a new
point is reached.  Thus when node $n_2$ is generated its $g$-value is not
computed as the length of the grid-constrained path used to reach it but rather
using the direct path $\langle n_1, n_2 \rangle$.

%\begin{figure}[tb]
% \begin{minipage}[b]{\0.45\linewidth}
%  \begin{center}
%    \input{tikz/ex1}
%  \end{center}
%  \caption{Example of an any-angle path}
%  \label{fig::ex1}
%  \end{minipage}
%\end{figure}

The problem with this approach is that the solution-cost estimate
(or $f$-value), from a parent node to each of its successors, may 
not be monotonically increasing.  The monotone condition is
necessary to guarantee that an optimal solution, if one exists, is always found.
For instance: Theta* can generate $n_2$ from the intermediate point $p = (3,3)$.
When $p$ is expanded we have $f(p) = d(n_1, p) + h(p, n_2) = 4.16$. 
To satisfy the monotone condition we require that $f(n_2) \geq 4.16$. However 
Theta* computes $f(n_2) = d(n_1, n_2) + h(n_2, n_2) = 4.12$.
Clearly $p$ should be expanded after $n_2$ but in this case the opposite occurs.  
In order to avoid this mistake we would need to consider, in addition to the
set of discrete points from the grid, all the points $y_i$ shown in Figure~\ref{fig::ex1}.
The problem is that the number of such points can be very large:
each edge of the grid, together with its discrete endpoints, 
forms a $[0, 1]$ interval that can be intersected by the optimal
path at any point $0 \leq \frac{w}{h} \leq 1$; here $w$ (resp. $h$) is an integer in
$\{0,\dots,W\}$ (resp.  $\{0,\dots,H\}$).
This is a set whose members are reducible to a Farey Sequence.
For any given $n$ (in our case $n = \max(W, H)$) the cardinality of the corresponding 
set of elements is known to be quadratic in $n$~\cite{concrete89}.
We are therefore motivated to consider an alternative approach: instead
of evaluating each $y_i$ node individually we will evaluate together
all the nodes from the corresponding interval in which each $y_i$ appears.


