\section{Symmetry Breaking In 4-Connected Grid Maps}
\label{sec::rsr::symm4c}

Trivial rooms which contain no interior nodes (for example rooms with a width $w$ or height $h$ 
$\leq 2$) are left unmodified by steps 2 and 3.
Figure \ref{fig-overview} shows an example of this process.
For each non-trivial room we prune $(w-2)\times(h-2)$ interior
nodes and, in the process, eliminate a large number of symmetric paths between 
nodes on the perimeter.
We claim that this approach preserves optimality when traversing across any arbitrary room.

\begin{lemma}
\label{thm-roomtraversal}
Let $R$ be an arbitrary rectangular room that is free of obstacles
and $m, n$ be two locations on its perimeter.
Then $m$ and $n$ can be connected optimally through a path that
mentions only nodes on the perimeter of $R$ and possibly involves
a macro edge.
\end{lemma}
\begin{proof}
\par
There are two distinct cases to consider.
Case 1 is when $m$ and $n$ are placed on the same side of the perimeter, or
on two orthogonal sides. 
To obtain an optimal path we can simply travel along the perimeter from $m$ to $n$.
Case 2 is when $m$ and $n$ are placed on opposite sides of the perimeter.
To obtain an optimal path we can simply follow the macro edge at $m$ 
and navigate directly to a node $m'$ located on
the same side of the perimeter as $n$. Then, go from $m'$ to $n$ along the perimeter.
The resultant path is optimal as its length is equal to the Manhattan distance between $m$ and $n$.
\end{proof}

A direct corollary to Lemma \ref{thm-roomtraversal} is that we can prune from consideration
all nodes from the interior of $R$ and limit ourselves to only searching nodes appearing along its perimeter. 
The only remaining consideration is how to deal with interior nodes that happen
to be the start or goal location for the search at hand.
We address this case in the following section.

