\section{Introduction}
\label{sec::introduction}
Grid-based pathfinding is a problem that often
appears in application areas such as robotics and computer games. 
%Many solution approaches exist; the most recent employ ideas from the
%literature of AI Search (e.g. ~\cite{pochter10,goldenberg10,yap11,urasKH13})
%and also Algorithmics (e.g.~\cite{storandt13,antsfeld12}). Such grid-based
Grids are popular with researchers because the encoding is
simple to understand and apply but the process of finding optimal paths
between arbitrary start-target pairs can be surprisingly challenging. At least
one reason for this difficulty can be attributed to the existence of 
symmetries: myriad in grid maps but less common in other domains such as
road networks. A path is considered symmetric when its individual steps 
(or actions) can be permuted in order to derive a new and equivalent path
that has identical cost.
In the presence of symmetry classical algorithms such as A* will waste much 
time looking at permutations of all shortest paths: from the start node to each expanded node.

Jump Point Search (JPS)~\cite{harabor11b} is a recent and very effective 
technique for identifying and eliminating path symmetries on-the-fly. 
JPS can be described as the combination of A* search with two simple 
neighbour-pruning rules. When applied recursively these rules
can improve the performance of optimal grid-based pathfinding by an order of 
magnitude and more -- all without any pre-processing and without the 
introduction of any memory overheads.

\input{table_bottleneck}

The efficiency of JPS depends on being able to quickly scan many nodes
from the underlying grid map in order to identify jump points.
On the one hand such a procedure can typically save many unnecessary
node expansions. On the other hand the same operation proceeds in a 
step-by-step manner and it can scan the same node multiple times during 
a single search. 
Consider Table~\ref{table::bottleneck}, where we give a comparative
breakdown of how JPS and A{*} spend their time during search.
The results are obtained by running
a large set of standard instances on three realistic game benchmarks
that appeared in the 2012 Grid-based Path Planning Competition. Observe that
JPS spends $\sim$90\% of its time generating successors (cf. $\sim$40\% for
A{*}) instead of manipulating nodes on the open and closed lists -- i.e.
searching.

In this paper we propose a number of ideas to improve the performance of Jump
Point Search. We focus on: (i) more efficient online symmetry breaking that
reduces the time spent scanning the grid; (ii) pre-computation strategies for
breaking symmetries offline; (iii) more effective online pruning strategies
that avoid expanding some jump points. We evaluate our ideas on three realistic
grid-based benchmarks and find that our enhancements can improve the
performance of Jump Point Search by anywhere from several factors to over one
order of magnitude.

