\chapter{Rectangular Symmetry Reduction}
\label{cha:rsr}
In this chapter we present Rectangular Symmetry Reduction (RSR): a graph pruning
algorithm for undirected uniform-cost grid maps which is fast, memory efficient,
optimality preserving and which can, in some cases, eliminate entirely the need
to search.  The central idea that we will explore involves the identification
and elimination of \emph{path symmetries} from the search space. 
To deal with symmetry RSR makes use of an off-line
empty rectangle decomposition that converts an arbitrary
undirected uniform-cost grid map into an equivalent one where only nodes
from the perimeter of each empty rectangle need to be explored during search.
We begin by introducing our idea in the context of 4-connected grid maps, a common
setting in video games and one which appears often in the AI literature.
We then turn our attention to 8-connected grid maps where the increase in
branching factor makes effective symmetry elimination more challenging. 
For this setting we develop a stronger symmetry breaking technique which can significantly
reduce the number of nodes that need to be explored during search. We also study a novel 
online pruning strategy which speeds up node expansion by selectively evaluating either 
all neighbours associated with a particular node or only a small subset.  
We prove that in each case both optimality and completeness are preserved.
\\ \newline
The contributions described in this chapter have been presented previously in
~\cite{harabor10,harabor11a,harabor11c}.

