\section{Discussion}
\label{cha::rsr::discussion}
In this chapter we study the problem of pathfinding in 4 and 8-connected grid
maps; two domains which appear regularly in modern video games and academic
literature.  We show that in such settings optimal search can be very
difficult because between any pair of nodes there exist many alternative paths
which are symmetric: that is the paths are identical save for the order in
which individual moves occur.  We presented RSR: a novel optimal offline
method for breaking such symmetries which is simple to understand and requires
no significant extra memory.  Our method involves decomposing a map into empty
rectangular rooms, pruning all nodes appearing in the interior and replacing
them with a set of \emph{macro edges} that facilitate optimal traversal from
the perimeter of any room to the perimeter of any other.  We also give an
online node insertion technique that extends these guarantees
 to arbitrary pairs of locations appearing in the original unmodified map.
\par
We evaluate the performance of our algorithm by running A* on a wide range of
realistic game maps including one well known set from the game \emph{Baldur's
Gate II}.  In many cases we are able to prune over 50\% of all nodes on a
given map and improve the average search time performance of A* by anywhere
from several factors to over one order of magnitude.  We then compare the
performance of RSR to to Swamps-based pruning~\citep{pochter09,pochter11} and
the Portal Heuristic~\citep{goldenberg10}-- two algorithms considered
state-of-the-art at the time of their publication and which are contemporaries
to RSR.

We show that Swamps-based pruning and RSR  have complementary strengths. In
particular we find that Swamps are more useful on maps with small open areas
while RSR becomes more effective as larger open areas are available on a map.
We also identify a broad range of instances where RSR dominates convincingly
and is clearly the better choice.  When we compare RSR to the enhanced Portal
Heuristic we find that our method exhibits similar or improved performance but
requires up to 7 times less memory.  We find that both Swamps and the Portal
Heuristic are complementary ideas to RSR and we suggest how they could be
easily combined.
\par
The effectiveness of RSR is strongly dependent on the topography of individual
maps: in the presence of large rooms or wide open areas (both commonly seen in
video games\footnote{For example, Blizzard's popular multi-player game
\emph{World of Warcraft}}) we can often compute optimal paths much faster than
searching on the original map.  On less favourable map topographies we achieve
more modest improvements.  However, since our method is orthogonal to existing
search techniques, it could be integrated as part of a larger framework
involving specialised heuristics or other speedup techniques; for example as
described in \citep{botea04,bjornsson05,bjornsson06}.
