\section{Time and Space Requirements}
Jump Point Search performs on-the-fly symmetry breaking by recursively travelling
along the map in a given direction and checking each node it encounters for the
presence of forced neighbours. In this section we analyse the time and space
complexity of these operations. We distinguish between \emph{straight jumps}
(i.e. where $\vec{d}$ is one of of the four cardinal directions) and 
and \emph{diagonal jumps} (where $\vec{d}$ is one of the four remaining directions).

\begin{lemma}
Any straight jump operation will visit a number of nodes at most equal to the
larger of $(h-1)$ ($h$ is the height of the map) or $(w-1)$ ($w$ is the width of the map).
Any diagonal jump operation will visit at most $(h \times w) - (h + w) + 2$ nodes.
\end{lemma}
\begin{proof}
Given an initial node $x$, Algorithm~\ref{alg::jps::jump} steps recursively in
a fixed direction direction $\vec{d}$ until one of three stopping conditions
are satisfied: (i) the procedure encounters the goal node (line 6); 
(ii) the procedure encounters a node with a forced neighbour (line 9); 
(iii) the procedure encounters an obstacle (line 3).  
In the case of a straight jump, the algorithm can proceed at most
until the edge of the map, which is considered an obstacle. Thus the maximum
number of steps that can be taken is equal to $(h-1)$ or $(w-1)$).  
In the case of a diagonal jump, Algorithm~\ref{alg::jump::jps}, before it can
recurse, must check for jump points in one of two straight directions. The
first time these two checks are performed the algorithm will visit at most $h
+ w - 1$ nodes. The second time these checks are performed the algorithm will
visit $h + w - 2$ nodes. There can be up to 
$n = \argmin \lbrace (h-1), (w-1) \rbrace$ steps 
taken before the edge of the map is reached.
\end{proof}

Upon visiting a node, Jump Point Search inspects the set of adjacent grid
neighbours. This operation involves up to eight memory access requests and
requires a constant amount of space.  Unlike A*, which must generate every
neighbour of every expanded node, Jump Point Search generates and expands in
most cases only a small subset. In the worst case every node has a forced
neighbour and must be expanded. Thus the search behaviour of JPS reduces to
that of A* on maps that contain little to no symmetry.
Figure~\ref{fig::jps::worstcase} shows an examples that approaches this
worst-case. We examine the relative performance of Jump Point Search and A* in
more detail in Section~\ref{cha::jps::results}.
