\chapter{Conclusion}
\label{cha::conclusion}

Pathfinding is a problem that has received significant attention from both
researchers and industrial practitioners. Despite numerous studies, many types
of pathfinding problems remain very challenging to solve. In the case of
mobile robots and computer games, where the world is often represented as a
grid, there exist two significant research challenges: (i) grids are dense and
contain many nodes which makes grid-optimal pathfinding difficult; (ii)
grid-optimal paths are often not Euclidean-optimal which is undesirable from
an efficiency perspective and also from an aesthetic perspective.

To address the first of these challenges we have developed Rectangular
Symmetry Reduction (RSR) and Jump Point Search (JPS): two novel and performant
pathfinding algorithms that speed up grid-optimal search by identifying and
eliminating from consideration paths that are symmetric permutations of each
other.  JPS and RSR can improve the runtime performance of classical
algorithms such as A{*} by anywhere from several factors to one and sometimes
two orders of magnitude -- all without extensive pre-processing or the
introduction of large memory overheads.

To address the second research challenge we have developed Anya: a novel
approach for computing Any-angle (i.e. Euclidean-optimal) paths on a grid map.
Previous attempts at computing such paths have either been online methods that
yield only approximate solutions or exact methods that require an offline
pre-computation step.  Anya is the first algorithm that, to the best of our
knowledge, combines the advantages of both approaches without the
disadvantages of either.

Our work represents a significant advancement of the state-of-the-art. With
RSR and JPS we have shown that optimal pathfinding on many of the most
challenging grid-based benchmarks from the literature, maps drawn from real
computer games, can be reduced to problems that require very little effort to 
solve. With Anya we have resolved an open question from the areas of Artificial 
Intelligence and Game Development: is there an Any-angle pathfinding algorithm
which is both online and optimal?  The answer is yes.

\newpage
