\section{Introduction}
\label{sec:introduction}
Pathfinding systems that operate on uniform-cost grid maps are common in the AI
literature and application areas such as robotics and real-time
video games.  Typical speed-up enhancements in such contexts include reducing
the size of the search space using abstraction \cite{botea04} and developing new
heuristics to more accurately guide search toward the goal \cite{sturtevant09}.
Though effective each of these strategies has shortcomings.  For example,
abstraction methods usually trade optimality for speed.  Meanwhile, improved
heuristics usually require significant extra memory.
\par 
My research proposes to speed up grid-based pathfinding by identifying
and eliminating symmetric path segments from the search space. 
Two paths are said to be symmetric if they are identical save for the order
in which the individual moves (or steps) occur. 
To deal with path symmetries I decompose an arbitrary
grid map into a set of empty rectangles and remove from each rectangle all
interior nodes and possibly some from along the perimeter.  A series of macro
edges are then added between selected pairs of remaining nodes in order to
facilitate provably optimal traversal through each rectangle.  The new
algorithm, Rectangular Symmetry Reduction (RSR), can speed up A* search by up to
38 times on a range of uniform cost maps taken from the literature.  In addition
to being fast and optimal, RSR requires no significant extra memory and is
largely orthogonal all existing speedup techniques.  When compared to the state
of the art, RSR often shows significant improvement across a range of
benchmarks.
