\section{Improved Heuristics}
\label{cha::lit::heuristics}
%Heuristic functions are employed in search to evaluate states in terms
%of merit. In the case of local search, heuristics are used to choose 
%a successor state from a large set of possible successors. In the case
%of informed search, heuristics provide estimates on the remaining distance 
%to the goal. We discuss a range of representative works for computing such 
%lower-bounds. This is in keeping with the scope of this thesis which is
%concerned with optimality-preserving pathfinding techniques.

%A heuristic, in the context of optimal pathfinding search, is a function that 
%estimates the distance from any given node to the goal. 
%
In the context of optimal search a heuristic $h$ is a lower-bound
cost-estimation function defined over states. Its purpose is to estimate
cost-to-go; i.e. to answer questions of the form ``how far is this node from
the target?".  Heuristics are useful if they can be computed efficiently (i.e.
polytime or better) and if they are accurate.  A popular default when
pathfinding in the plane is $h_{SLD}$ or the Straight Line Distance heuristic.
$h_{SLD}$ is consistent, admissible and runs in constant time (see  Section
\ref{cha::lit::search} for a definition of these terms).  In the absence of
obstacles $h_{SLD}$ is perfect but in more complex environments it can
dramatically underestimate optimal distances between two arbitrary points;
e.g. as seen in~\citep{goldberg05}.

Many works focus on improving the accuracy of $h_{SLD}$ without negatively
impacting its running time. This approach usually translates into faster
search algorithms. However, there are limits.  A number of theoretical
models~\citep{pohl77,helmert08} have shown that optimal search strategies
employing even almost perfect heuristics, i.e. those having only a small
additive constant for error, must expand, in the worst case, an exponential
number of nodes before reaching the goal.  A similar result can also be
derived for the average case~\citep{pearl84}.  The models used in these
theoretical works often employ certain simplifying assumptions.  They
nevertheless align well with domain models that appear in pathfinding search;
e.g. constant branching factor, uniform-cost edges and a singleton goal state.
Despite such seemingly discouraging results researchers have demonstrated
that, in many pathfinding domains of practical interest
(e.g.~\citep{sturtevant12}), better heuristic estimates can dramatically
improve the performance of optimal search.

One idea for improving heuristic accuracy is to take into account domain
specific movement rules.  $h_{MD}$ (Manhattan Distance) and $h_{OD}$ (Diagonal
or Octile Distance) are two such heuristics; they retain all the properties of
$h_{SLD}$ but provide better lower-bound estimates when pathfinding in square
grids. $h_{MD}$ computes a lower-bound on the number of horizontal and vertical
steps still needed to reach the target node. $h_{OD}$ computes a similar
lower-bound but assumes that diagonal steps are also allowed.  Similar
domain-specific heuristics have been developed for pathfinding in hexagonal
grids~\citep{yap02} and more broadly for optimally solving large combinatorial
puzzles~\citep{korf96}.

Another approach to improving heuristic accuracy involves pre-computing
distance databases.  A large family of related algorithms, sometimes called
\emph{memory heuristics}, has been described in the
literature~\citep{goldberg05,bjornsson06,sturtevant07,felner09,goldenberg10,anderson10}.
ALT~\citep{goldberg05} is a typical representative. During a preprocessing
step ALT selects from the map a set of \emph{landmark} nodes and then computes
a database of optimal distances from each node to every landmark. Given such a
database it can be shown that admissible estimates between a pair of nodes can
be computed by subtracting the distances from the two nodes at hand to a fixed
landmark.  ALT takes as its heuristic estimate the maximum difference over all
landmarks.  Further enhancements to this type of approach involve the
combination of distance databases with spatial abstraction. Such examples
include the Gateway Heuristic~\citep{bjornsson06} and the Portal
Heuristic~\citep{goldenberg10}. Memory heuristics are very fast, typically
constant time, and can improve the performance of optimal search by anywhere
from several factors to an order of magnitude. Their primary disadvantages are
often lengthy pre-processing times and significant space overheads.  This
largely excludes memory heuristics from being applied in many popular
pathfinding settings, including robotics and computer games.

In a recent paper~\cite{rayner11} describe a technique for computing entire
families of Euclidean heuristics. Their approach involves
embedding a spatial network graph into a manifold. Computing the embedding
requires solving a constrained optimisation problem that minimises heuristic
error. The authors show that their approach produces very accurate results in
practice but solving the optimisation problem can require significant
preprocessing time and space.  

SILC~\citep{sanka05} and Compressed Path Databases (CPDs) are two very
powerful memory-based techniques which are related to but which are not
instances of memory heuristics. Rather than computing a database of distances
between selected pairs of points however (i.e. a heuristic) these approaches
constructs a pathfinding oracle using the results of an exact all-pairs
shortest-path computation.  A CPD for example can be described as a highly
compressed set of tables that store the first move on the optimal path between
any pair of nodes in a graph. Through a simple process of recursive look-ups
CPDs can extract any optimal path in near-linear-time and without employing
any state-space search.  SILC and CPDs are among the fastest pathfinding
techniques today but because they require substantial amounts of memory and
pre-computation they are not applicable in many popular pathfinding settings,
including games.

%Pattern Databases (PDBs)~\cite{culberson96} are a powerful method for automatically constructing
%memory-based heuristics from domain abstractions. Though often employed in solving large 
%combinatorial problems, PDBs cannot be feasibly applied in pathfinding as the goal state is 
%not fixed. Block A*~\cite{yap11} is one attempt at applying PDBs 
