\section{Dominance Detection}
\label{cha::lit::dominance}
In many pathfinding domains, and especially in gridmaps, arbitrary problem instances rarely
have only a single optimal solution. These solutions can be symmetric to each other 
(c.f. Section~\ref{cha::lit::symmetry}) or they can simply be equivalent in terms of cost.
Pathfinding instances that have many equivalent solutions are difficult to solve; even for 
efficient search algorithms such as A*. In such cases, before even one optimal path can be found,
A* must usually generate (and often expand) every node on every other equivalent optimal path.
This is wasteful and prevents A* from making real progress toward the target. 
A number of works can be found in the literature of Heuristic Search that identify and
eliminate equivalent paths. Such algorithms are known as \emph{graph pruning} 
or \emph{dominance detection} techniques. We briefly outline them here.

\begin{definition}
A path $\pi$ \emph{dominates} another path $\pi'$ if $cost(\pi) \leq cost(\pi')$. 
If $cost(\pi) < cost(\pi')$ then $\pi$ is \emph{strictly dominant}.
\end{definition}

The Dead-end Heuristic~\citep{bjornsson06} and Swamps~\citep{pochter09,pochter10} are two very
similar a graph pruning techniques that can eliminate from consideration many dominated and strictly
dominated paths.  Both rely on an offline preprocessing phase that decomposes a given map into
obstacle-free areas.  During online search each of these two algorithms consults the decomposed map
in order to identify areas that are relevant for the instance at hand and areas that can be ignored
entirely because exploring them could not improve the length of any path.
%It can be seen as a technique for detecting areas that don't have to be searched
%in the instance at hand and, as before, is complementary to our work.

MSA*~\citep{bolanca09} is another recent pruning technique which is orthogonal to both Swamps and
the Dead-end Heuristic.  Where those algorithms identify areas that can be ignored during search,
MSA* generates, on the fly, macro-edges that facilitate fast travel through areas that do have to be
searched.  It relies on a preprocessing step that decomposes a given grid map into a series of empty
rectangular rooms. The key idea is that each such room can be traversed in a single macro step. MSA* 
is similar in spirit to Rectangular Symmetry Reduction; an alternative pruning
algorithm that we introduce in Chapter~\ref{cha::rsr}.  While our work can consistently speed up A*
search, MSA* is only able to achieve this in some cases.  It is also worth noting that MSA* uses a
different empty room decomposition method from the one described in our work.

A different technique for pruning the search space is to identify \emph{dead} and \emph{redundant}
cells~\cite{sturtevant10b}.  Developed in the context of learning-based heuristic search, this
method speeds up search only after running multiple iterations of an iterative deepening algorithm.
During each iteration the algorithm stores the $g$-value associated with each expanded node and
prunes from subsequent iterations all nodes that were found to have zero $g$-cost-increasing
neighbours.

Fast Expansion~\cite{sun09} is another related work that speeds up A* pathfinding search. 
This algorithm detects when a newly generated (or newly relaxed) node has an $f$-value that 
dominates the $f$-value of the best node on the open list. The idea is to expand such nodes 
immediately and avoid unnecessary operations on the open list.
