\section{Future Work}
\label{cha::conclusion::future}
We discuss future work in terms of our two main contributions: Symmetry breaking
in pathfinding search and optimal approaches for Any-angle pathfinding.

\subsection{Symmetry Breaking}
One interesting direction for further work involves stronger pruning rules for
Jump Point Search on both weighted and unweighted grid maps.  In
Chapter~\ref{cha::jps::weighted} we have given one simple suggestion for
adapting the existing algorithm to weighted grids: simply stop whenever any
neighbouring tile has a different terrain type than the current node.  A more
general approach is to explicitly calculate the weighted cost of local paths:
from the parent node to each neighbouring node.  The advantage is that we do
not necessarily need to stop each time the path transitions from one weighted
region to another. We need to be careful however to balance the additional
time required to explicitly compute the costs of each local path vs. the time
savings from performing fewer node expansions.

In the case of unweighted grid maps we believe stronger symmetry breaking
rules are possible which will allow us to jump over at least some of the
remaining nodes currently expanded by Jump Point Search. For example we might
consider pruning a node $n$ if all its successors have the same $f$-value as
$n$; i.e.  we can try to keep jumping as long as we are heading in the
direction of the goal.  A stronger variant of this idea is to keep jumping as
long as we are heading in the same direction to the one used to reach $n$ 
(or in a new direction which is a component of the original). For example,
suppose we reach node $n$ by jumping in direction $\vec{d}$.  If all the
successors of $n$ can be reached by also jumping in direction $\vec{d}$ or in
another direction which is a component of $\vec{d}$ then we can consider
pruning $n$ and continuing to recurse in each of these directions. It is
likely that this procedure will increase in the branching factor at $n$ but we
posit that fewer node expansions are required overall because we do not
necessarily need to stop each time the path turns.  A similar idea is
described in~\citep{urasKH13} where the authors also exploit path symmetries
to speed up search -- though their approach is is offline only.

Another interesting direction for future work is to apply Jump Point Search 
to other types of grids, such as hexagons or texes~\citep{yap02}. We propose
to achieve this by developing  a series of pruning rules analogous to those
given for square grids.  As the branching factor on these domains is lower
than square grids, we posit that jump points could be even more effective 
than we have observed for square grids.

Finally, synthesising JPS with complementary speedup techniques from the
literature appears to be a promising line of research. For example JPS could
be used to speed up optimal search in an implementation of
Swamps~\citep{pochter10} or to speed up start and target insertion in an
approximate hierarchical pathfinder such as HPA{*}~\citep{botea04}.

\subsection{Any-angle Pathfinding}
An obvious direction for further work is a concrete implementation of Anya
together with an empirical evaluation. This is a topic of current research.

Another interesting direction is to generalise the theoretical results from
Anya to the problem of finding Euclidean-optimal paths in continuous planar
environments with polygonal obstacles -- rather than the square obstacles of
the type found in grid maps. Such a generalisation could be achieved by (i) 
using a grid to tessellate the environment and (ii) testing if any obstacles
intersect the current interval as we move it from one row of the grid to another.
Each time we detect an intersection we generate a successor interval whose y-axis
is the same as the obstacle rather than the y-axis of the next row.
