\section{Summary}
\label{cha::conclusion::summary}
We study optimal pathfinding in discrete and static two-dimensional
environments. Our target applications include mobile robot navigation and
pathfinding in computer games, both settings where the world is commonly
represented as a grid. Our objectives throughout this thesis have been to: (i)
find the shortest path; (ii) as quickly as possible; (iii) as economically as
possible with respect to available resources such as memory and
pre-computation time.

We identified two significant challenges that arise when trying to find optimal
paths on grid domains: (i) grids are dense and finding a grid-optimal path often
means expanding very many nodes; (ii) paths which are grid-optimal are often
not Euclidean-optimal which is undesirable from both an an efficiency
perspective and an aesthetic perspective. We address the first of these
challenges in Chapter~\ref{cha::rsr}, Chapter~\ref{cha::jps} and
Chapter~\ref{cha::jps2}.  We address the second of these challenges in
Chapter~\ref{cha::anya}.

In Chapter~\ref{cha::rsr} we identify one significant factor that makes
pathfinding in grids challenging: the existence of equivalent permutations 
(i.e. symmetries) for many shortest paths in a grid. We formalise this idea by defining concretely
what it means for two paths to be symmetric. We then give a description of and
experimental evaluation for an offline symmetry-breaking approach called
Rectangular Symmetry Reduction (RSR). We show that RSR can improve the
performance of the classical A{*} algorithm by several factors in most of our
benchmark domains and up to one order of magnitude in some other cases.
We then compare RSR with two contemporary pathfinding algorithms, 
Swamps~\citep{pochter10} and the Portal Heuristic~\citep{goldenberg10}.
We find that RSR has complementary strengths with these approaches and we
identify many instances where RSR dominates convincingly.

In Chapter~\ref{cha::jps} we present Jump Point Search (JPS): an alternative
symmetry breaking procedure which selectively expands only certain nodes on
a grid map called \emph{jump points}.  JPS is recursive in nature,
guaranteed optimal and applied entirely online. It requires no pre-processing
and introduces no memory overheads. JPS can improve the performance of standard
A{*} by one order of magnitude and more in each of our benchmark domains. It
compares favourably with and convincingly dominates contemporary optimal
speedup techniques such as Swamps. It is also competitive with the non-optimal
hierarchical pathfinding method HPA{*}.  JPS is unique in the pathfinding
literature in that it has very few disadvantages: it is simple, yet highly
effective; it preserves optimality, yet requires no extra memory;  it is
extremely fast, yet requires no pre-processing. We are unaware of any 
other algorithm which has all these features.

In Chapter~\ref{cha::jps2} we present several enhancements that further
improve the performance of Jump Point Search. The first enhancement allows JPS
to prune from consideration certain types of nodes known as intermediate jump
points.  The second enhancement allows JPS to consider ``blocks'' of nodes at
one time when breaking symmetries (cf. individual nodes).  The third
enhancement is an offline pre-processing technique that speeds up search by
identifying jump points apriori.  We show in an empirical evaluation that
these improvements have a strong positive effect on Jump Point Search,
improving an already performant algorithm by anywhere from several factors to
more than one order of magnitude.  We compare our approach with two variants
of SUB~\citep{urasKH13}: a recent and very fast pathfinding approach that also
breaks path symmetries but only during an offline pre-processing step. We find
that JPS and SUB have complementary strengths and we identify many instances
where one or more of our enhanced JPS variants are faster.

In Chapter~\ref{cha::anya} we turn our attention to Any-angle pathfinding.
This is a problem that takes as input two points from a grid and asks for a
Euclidean-optimal path connecting them. We describe Anya: a novel approach to
Any-angle pathfinding which involves considering sets of states together as an
interval. From each interval we select a single representative point which we
use to compute an $f$-value for the entire set.  During search intervals are
projected from one row of the grid to another until the target is reached. We
give theoretical results showing Anya always finds a Euclidean-optimal path if
one exists. Moreover, Anya does so entirely online and without any
pre-processing.  We are unaware of another other approach which guarantees
 these desirable characteristics.
