\section{Problem Definition}
A \emph{gridmap} is a structure composed of atomic square cells.
%, each of which represent a unique area in the environment. 
Each grid cell is called an \emph{octile}, being connected to $k$ neighbours, where  $0 \leq k \leq 8$. 
%\par \indent
Each octile is either blocked or traversable. 
Blocked octiles are called \emph{hard obstacles}, since no agent can occupy them.
Each traversable octile, $t$, is associated with a particular terrain type, $terrain(t) \in T$ where $T$ is the set of all possible terrains and there are $r = |T| \geq 1$ possible terrains.
%\par \indent
A gridmap is representable as a graph $G = (V, E)$ where each traversable octile generates one node $v \in V$ and each octile adjacency is represented by an edge $e \in E$.
\par \indent
An \emph{agent} is any entity attempting to move across a gridmap. 
Every agent is square in shape and has a size $s \geq 1 : s \in S$ where $S$ is the finite set of all agent sizes defined for a problem.
An agent occupies $s \times s$ octiles, which together correspond to its current location. 
%\par \indent
Every agent has a terrain traversal \emph{capability} $c \subseteq T$ which comprises a combination of one or more terrains. Let $C \subset 2^T$ be the set of the capabilities $c$ of all agents.
An agent can never occupy an octile whose terrain type is not included in its capability.
Thus an $s \times s$ location is traversable by an agent of size $s$ and capability $c$ if the terrain types of all location's octiles are included in $c$.
An agent can move in a cardinal direction between two $s \times s$ locations $l_1$ and $l_2$ if (1) both $l_1$ and $l_2$ are traversable by the agent and (2) the total displacement between $l_1$ and $l_2$ is limited to the length or width of a single octile. 
A diagonal move is allowed only if there exists an equivalent (but longer) two-step move using cardinal directions.
\par \indent
A \emph{problem instance} (or \emph{query}) is defined as a pair of locations, start and goal, associated with an agent. A problem is valid if at least one path exists between the locations comprising only octiles traversable by the agent. 
